### 2021-04-18 Chapter-3/Chapter-3.tex
Updates from Overleaf

The root cause of most side-channel attacks can been as a result of the combination of the hardware design and the vulnerable software. Existing countermeasures can be classified into two categories: fixing the software and adopting new hardware. Based on the discussion in \S\ref{chapter1} and \S\ref{chapter2}, patching bugs in software is usually easier than adopting new hardware to defend against side-channel attacks. In order to eliminate those leakage sites, developers often need to identify potential leakage sites from the code base manually. However, the manual process is tedious and error-prone. Recent studies~\cite{203878} also suggest fixing old vulnerabilities can sometimes introduce new leakages.

Recent work has made good progress in identifying side-channel leakages automatically. Some tools (e.g., CacheD, CaSym) have successfully identified unknown leakage sites from software products automatically. However, those tools have the following limitations.

First, although some tools can find side-channel leakages in real-world software products, they can only analyze one code fragment at a time due to the expensive performance overhead. As a result, users of those tools sometimes need to manually cut off some irrelevant code based on their past experience. The trimming process is tedious and needs domain knowledge of the target software (e.g., which part of the code is more likely to have side-channel leakage sites). More importantly, if many leakages sites are on the trimmed code, those tools will miss those leakage sites as well.

Second, many tools perform the analysis at the level of intermediate representations (IR) instead of machine code. It is a design decision to facilitate the implementations. While analyzing the IRs can simplify the implementation, it is not a suitable design choice for the side-channel analysis. In reality, side-channel leakages are a pretty low-level issue and only the low-level analysis can give the most accurate results. For example, the IR-level branches is not necessarily a superset or a subset of machine-code level branches. Besides, compiler optimizations can eliminate the IR-level branches like conditional moves and the converse could also happen. Moreover, translating the machine code into IRs can cause a significant overhead for the trace analysis, as we will discuss in the dissertation.

To overcome the above problems, we propose a fast and precise method to detect the side-channel leakages in real-world software products. Different from previous methods, our tool analyzes on the machine code, which can give more precision than traditional IR-based approaches.  We examine the bottleneck of current symbolic execution approaches and optimize it to work on real-world cryptography systems. The evaluation results show that our tool can identify previous side-channel leakages, as well as find new leakages. Compared to recent tools, our tool is 3-100x faster while finding all the leakages when we evaluate on the same benchmarks.

@@

CPUs process data in a much faster speed than the main memory (DRAM) can supply. Modern CPUs adopt a hierarchy memory to bridge the performance gap between the CPUs and the main memory. By storing extra copies of data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.

Figure~\ref{fig:memory_hierarchy} shows the overview of the hierarchy memory. For a CPU with multiple cores, each core has two private level-1 (L1) cache, an instruction cache (iCache), and a data cache (dCache). Because instructions and data have different access patterns, separating iCache and dCache makes it possible for CPUs to fetch the code and data and improve performance simultaneously. Followed by the level-1 cache, each core also has the unified private level-2 cache for both the code and the data. The level-3 cache is the last level cache (LLC). The LLC is shared among all the cores. The main memory is the bottom-most under the memory hierarchy.
\begin{figure}
  \centering
  \includegraphics[width=.5\columnwidth]{./figures/chapter3/architecture.pdf}
  \caption{Computer memory hierarchy. The hierarchy is designed to minimise the access time with the relatively low cost. It is the root cause of many side-channel attacks.}\label{fig:memory_hierarchy}
\end{figure}

>>>>

The cause of most side-channel attacks can been as the combination of the hardware design and the vulnerable software. Existing countermeasures can be classified into two categories: fixing the software and adopting new hardware. Based on the discussion in \S\ref{chapter1} and \S\ref{chapter2}, fixing side-channel leakage sites in software is usually easier than adopting new hardware to defend against side-channel attacks. In order to eliminate those leakage sites, developers need to find potential leakage sites from the large code base manually. However, the manual process is tedious and error-prone. Recent work~\cite{203878} also suggests fixing old vulnerabilities can sometimes introduce new leakages.

Recent work has made good progress in detecting side-channel leakages automatically. Some tools (e.g., CacheD, CaSym) have successfully identified unknown leakage sites from software products automatically. However, those tools have the following limitations.

First, although some tools can find side-channel leakages in real-world software products, they can only analyze one code fragment at a time due to the expensive performance overhead. As a result, users of those tools sometimes need to cut off some irrelevant code based on their experience manually. The trimming process is tedious and needs domain knowledge of the target software (e.g., which part of the code is more likely to have side-channel leakage sites). More importantly, if many leakage sites are on the trimmed code, those tools will miss those leakage sites as well.

Second, many tools perform the analysis at the level of intermediate representations (IR) instead of the machine code. It is a design decision to facilitate the implementations. While analyzing the IRs can simplify the implementation, it is not a suitable design choice for the side-channel analysis. In reality, side-channel leakages are a pretty low-level issue and only the low-level analysis can give the most accurate results. For example, the IR-level branches is not necessarily a superset or a subset of machine-code level branches. Besides, compiler optimizations can eliminate the IR-level branches like conditional moves and the converse could also happen. Moreover, translating the machine code into IRs can cause a significant overhead for the trace analysis, as we will discuss in the dissertation.

To overcome the above problems, we propose a fast and precise method to detect the side-channel leakages in real-world software products. Different from previous methods, our tool analyzes on the machine code, which can give more precision than traditional IR-based approaches.  We examine the bottleneck of current symbolic execution approaches and optimize it to work on real-world cryptography systems. The evaluation results show that our tool can identify previous side-channel leakages, as well as find new leakages. Compared to recent tools, our tool is 3-100x faster while finding all the leakages when we evaluate on the same benchmarks. In addition, our tool finds new side-channel vulnerabilities that are missed by the previous work.

@@

During the evolution of the modern computer architecture, researchers find that CPUs process data in a much faster speed than the main memory (DRAM) can supply. As a result, modern CPUs adopt a hierarchy memory architecture to bridge the performance gap between the CPUs and the main memory. By storing extra copies of recently accessed data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.

Figure~\ref{fig:memory_hierarchy} shows the overview of one example of the hierarchy memory architecture. For a CPU with multiple cores, each core has two private level-1 (L1) cache, an instruction cache (iCache), and a data cache (dCache). Because instructions and data have different access patterns, separating iCache and dCache makes it possible for CPUs to fetch the code and data and improve performance simultaneously. Followed by the level-1 cache, each core also has the unified private level-2 cache for both the code and the data. The level-3 cache is the last level cache (LLC). The LLC is shared among all the cores. The main memory is in the bottom-most under the memory hierarchy.
\begin{figure}
  \centering
  \includegraphics[width=.5\columnwidth]{./figures/chapter3/architecture.pdf}
  \caption{Computer memory hierarchy. The hierarchy is designed to minimise the access time with the relatively low cost. It is the root cause of many side-channel attacks.}\label{fig:memory_hierarchy}
\end{figure}
